A Multi-Modal Model of Object Deformation under Robotic Pushing

### 2016-09-09 twostagedo.tex
changed title (again)
bibliography etc

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
% could we change the title to this? What do you think? I wanted to get the modular idea in there.
\title{A Multi-Modal Model of Object Deformation for Robotic Pushing
%A Multi-Modal Model for Prediction and Classification of Object Deformation during Robotic Manipulation
}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

@@

\section{Background}
\label{sec:background}
This work focuses on learning to predict what happens when an elastic or plastic object is pushed by a robot finger. These predictions include the response forces and the deformations of the object's shape over many future steps. The predictive models can be used to classify materials, even when the interactions (e.g. the contact point) are novel. Although there \comment{is a large body of work on deformable object tracking, some of which makes use of forces, models and predictions to improve tracking accuracy \cite{Chan1994, Greminger2008, Alkkiomaki2009}, those predictions are typically used only for the next frame and can not be used for robotic planning, where predictions must be made many steps into the future \cite{Cretu2012}.  Others like \cite{Malassiotis1998, Cremers2006} make use of templates or make assumptions about the shape of the objects that would not work with highly deformable objects like plasticine.  There is also} an abundant literature in industrial robotics for modelling 1D and 2D materials (e.g. string, hair, metallic sheet and textile), but there is little research about predicting the deformation of 3D deformable objects \cite{Khalil2010review}.

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
\bibliographystyle{IEEEtranS}
% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{twostagedo}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
% \begin{thebibliography}{1}
% 
% \bibitem{IEEEhowto:kopka}
% H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
%   0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
% 
% \end{thebibliography}

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
% could we change the title to this? What do you think? I wanted to get the modular idea in there.
\title{A Multi-Modal Model of Object Deformation under Robotic Pushing
%A Multi-Modal Model for Prediction and Classification of Object Deformation during Robotic Manipulation
}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

@@

\section{Background}
\label{sec:background}

\comment{It is known that the human motor system uses predictive (or forward) models of the effects that motor actions have on sensory state \cite{flanagan03,flanagan06,johansson92}. These are believed to be particularly important for dexterous manipulation. In robotics, prediction of physical interaction is a well studied but incompletely solved problem. There is a large body of work on the effects of pushing on rigid objects. This includes physics based models \cite{mason_manipulator_1982,lynch_mechanics_1992,peshkin_motion_1988,mason_mechanics_2001} and learning approaches \cite{montesano08,moldovan12,hermans11,fitzpatrick_learning_2003,ridge2010self,kroemer2014,Stoytchev_affordances_2008,mericli2014, scholz2010combining,kopicki-etal-icra11,kopicki2016learning,belter2014iros}. These predictive models have many applications, including visual tracking \cite{morwald2011icra, duff2011icra, pham2015capturing} and push planning \cite{stillman08ijrr,Dogar_2010,lynchmason96,zitoetal-iros12,Cosgun2011}.}

\comment{There is much less work in robotics on predicting the behaviour of deformable objects under manipulation. This paper focuses on learning to predict what happens when an elastic or plastic object is pushed by a robot finger.} These predictions include the response forces and the deformations of the object's shape over many future steps. The predictive models can be used to classify materials, even when the interactions (e.g. the contact point) are novel. Although there \comment{is a large body of work on deformable object tracking, some of which makes use of forces, models and predictions to improve tracking accuracy \cite{Chan1994, Greminger2008, Alkkiomaki2009}, those predictions are typically used only for the next frame and can not be used for robotic planning, where predictions must be made many steps into the future \cite{Cretu2012}.  Others like \cite{Malassiotis1998, Cremers2006} make use of templates or make assumptions about the shape of the objects that would not work with highly deformable objects like plasticine.  There is also} an abundant literature in industrial robotics for modelling 1D and 2D materials (e.g. string, hair, metallic sheet and textile), but there is little research about predicting the deformation of 3D deformable objects \cite{Khalil2010review}. We now review the most closely related work to that presented here.

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
\bibliographystyle{IEEEtranS}
% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{twostagedo,jlw}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
% \begin{thebibliography}{1}
% 
% \bibitem{IEEEhowto:kopka}
% H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
%   0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
% 
% \end{thebibliography}
